### 2013-09-30 src2/ifl/paperThesis.tex
apa

\documentclass[10pt]{llncs}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}

\usepackage{alltt}
\usepackage{placeins}

\usepackage{fancyvrb}

@@

\begin{document}

\title{Obsidian:\\A Domain Specific Embedded Language\\for Parallel Programming of Graphics Processors}

\author{Joel Svensson \and Mary Sheeran \and Koen Claessen}
\institute{Chalmers University of Technology, G\"oteborg, Sweden}

\date{}
\maketitle
\begin{abstract}

@@

\end{abstract}
\input{intro}
\input{combinators}   %% uncomment when file available
\input{GPUs}           %% I decided to put a separate section on GPUs, rather
                       %% than trying to cover it in the intro.

\input{obsidian}
\input{results}
\input{related}
\input{futurework}
\input{conclusion}
\bibliographystyle{plain}
\bibliography{ifl08}

\end{document}

>>>>

%\documentclass[10pt]{llncs}

%\usepackage{amsmath}
%\usepackage{graphicx}
%\usepackage{subfigure}

%\usepackage{alltt}
%\usepackage{placeins}

%\usepackage{fancyvrb}

@@

%\begin{document}

%\title{Obsidian:\\A Domain Specific Embedded Language\\for Parallel Programming of Graphics Processors}

%\author{Joel Svensson \and Mary Sheeran \and Koen Claessen}
%\institute{Chalmers University of Technology, G\"oteborg, Sweden}

%\date{}
%\maketitle

\section*{Abstract}

@@

%\end{abstract}
\input{./ifl/intro}
\input{./ifl/combinators}   %% uncomment when file available
\input{./ifl/GPUs}           %% I decided to put a separate section on GPUs, rather
                       %% than trying to cover it in the intro.

\input{./ifl/obsidian}
\input{./ifl/results}
\input{./ifl/related}
\input{./ifl/futurework}
\input{./ifl/conclusion}
%\bibliographystyle{plain}
%\bibliography{ifl08}

%\end{document}

### 2013-09-30 src2/thesis.tex
apa

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{lingmacros}
\usepackage{subfig}

@@

\section*{\centering Expressive Array Constructs in an Embedded GPU Kernel Programming Language}

@@

\section*{\centering Simple and Compositional Reification of Monadic Embedded Languages}

@@

\section{Paper2}

%\input{}

>>>>

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage{lingmacros}
\usepackage{subfig}

@@

% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

\chapter{Obsidian: A Domain Specific Embedded Language for Parallel Programming of Graphics Processors}
%\addcontentsline{toc}{chapter}{Obsidian: A Domain Specific Embedded Language for
%Parallel Programming of Graphics Processors}

\begin{center} 
Bo Joel Svensson, Mary Sheeran, Koen Claessen
\end{center}

\input{./ifl/paperThesis}

% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

\chapter{Obsidian: GPU Computing Using Haskell}
%\addcontentsline{toc}{chapter}{Obsidian: GPU Computing Using Haskell}

\begin{center} 
Bo Joel Svensson, Koen Claessen, Mary Sheeran
\end{center}

\input{./papp/paperThesis}

% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

\chapter{Expressive Array Constructs in an Embedded GPU Kernel Programming Language}
%\addcontentsline{toc}{chapter}{Expressive Array Constructs in an Embedded GPU Kernel Programming Language}

@@

% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

\chapter{Counting and Occurrence Sort for GPUs using an Embedded Language}
%\addcontentsline{toc}{chapter}{Counting and Occurrence Sort for GPUs using an Embedded Language}

\begin{center} 
Josef Svenningsson, Bo Joel Svensson, Mary Sheeran 
\end{center}

\input{./csort/paperThesis}

% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

\chapter{Simple and Compositional Reification of Monadic Embedded Languages}
%\addcontentsline{toc}{chapter}{Simple and Compositional Reification of Monadic Embedded Languages}

@@

% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

\chapter{Parallel Programming in Haskell Almost for Free}
%\addcontentsline{toc}{chapter}{Parallel Programming in Haskell Almost for Free}

\begin{center} 
Bo Joel Svensson, Mary Sheeran
\end{center}

\input{./embarbb/paperThesis}
